### 2022-10-24 manuscript.Rmd
Move Figure 2 to Supplementary Information

The experiment consisted of three phases (see Figure \@ref(fig:fig1)A).
In the *pre-insight* phase, after written informed consent had been obtained and the EEG had been prepared, all 240 familiar and unfamiliar objects were presented once in random order and without any keywords.
Each trial consisted of a fixation cross presented in the middle of the screen for 0.5 s, followed by the presentation of the object until participants made a response or until a time out after 3 s.
The inter-trial interval was 0.5 s and participants took a self-timed break after each block of 60 objects.
The task, which was kept the same across all three phases of the experiment, was to classify each object using one of four response alternatives:
(a) *Ich weiß was das ist oder habe eine starke Vermutung* [I know what this is or have a strong assumption],
(b) *Ich habe eher eine Vermutung, was das ist* [I rather have an assumption what this is],
(c) *Ich habe eher keine Vermutung, was das ist* [I rather have no assumption what this is], or
(d) *Ich weiß nicht, was das ist, und habe auch keine Vermutung* [I don’t know what this is and have no assumption].
Participants were asked to respond as quickly and as accurately as possible by pressing one out of four buttons with the index or middle finger of their left or right hand, respectively.
The mapping of the rating scale to the four buttons (left to right or right to left) was counterbalanced across participants.

@@

```{r, fig1, cache=!run$figures, fig.height=12, fig.cap="(ref:figure-1-caption)"}
# Create Figure 1
plot_fig1(files_dir, evokeds, config, channel_locations, models)
```

(ref:figure-1-caption) Experimental design and ERP results.
***A***, In the pre-insight phase, participants were presented with 120 unfamiliar objects and indicated if they knew what kind of object they were viewing.
In the insight phase, half of these objects were presented with matching keywords (in red color for illustration), leading to semantically informed perception, and the other half with non-matching keywords (in blue color for illustration), leading to naive perception.
In the post-insight phase, the same objects were presented again without keywords.
***B***, ***C***, ***D***, ERP waveforms and scalp topographies for the P1 component (100--150 ms, ***B***), for the N170 component (150--200 ms, ***C***), and for the N400 component (400--700 ms, ***D***) for objects with semantically informed perception versus naive perception within the three different phases.
Semantically informed perception was associated with more negative amplitudes in the N170 component during the insight phase, less negative amplitudes in the N400 component during the insight and post-insight phases, and more positive amplitudes in the P1 component during the post-insight phase.
The time windows and channels for quantifying the ERP components are highlighted by the gray areas in the ERP waveforms and by the black markers on the scalp topographies, respectively.
Colored ribbons around the ERP waveforms show ± 1 standard error of the mean across participants.
Ampl. = amplitude.\newline
\* $p_\text{corr} < .05$. \*\* $p_\text{corr} < .01$. \*\*\* $p_\text{corr} < .001$.

@@

We first excluded from all further analyses those objects for which the participant had responded with "I know what this is" in the pre-insight phase (i.e., before any keywords were presented).
This led to the exclusion of an average of `r mean(objects_per_condition$Exclude_known)` objects per participant (= `r percent(mean(objects_per_condition$Exclude_known) / 120, accuracy = 0.1)` of all unfamiliar objects).
Next, to delineate semantically informed and naive perception, the assignment of the remaining objects to one of these two conditions was co-determined by our experimental manipulation (matching versus non-matching keywords) and the behavioral response of the participant in the insight phase (see Figure \@ref(fig:fig1)A).
Objects were assigned to the semantically informed condition if and only if they were presented with matching keywords and the participant responded with knowing what the object was or having an assumption.
This was the case for an average of `r mean(objects_per_condition$Informed)` objects per participant (= `r percent(mean(objects_per_condition$Informed) / 60, accuracy = 0.1)` of objects presented with matching keywords).
Complementarily, objects were assigned to the naive condition if and only if they were presented with non-matching keywords and the participant responded with not knowing what the object was or having rather no assumption.
This was the case for an average of `r mean(objects_per_condition$Naive)` objects per participant (= `r percent(mean(objects_per_condition$Naive) / 60, accuracy = 0.1)` of objects presented with non-matching keywords).
This same assignment of objects to conditions based on the insight phase was carried over to the pre-insight and post-insight phases for each participant individually.
This allowed us to test, on the one hand, if the objects from both conditions differed in important aspects even before any keywords were presented (pre-insight phase) and, on the other hand, if the semantic understanding acquired in the insight phase had any down-stream effects on the subsequent perception of the objects (post-insight phase).

@@

In the pre-insight phase, when objects were unfamiliar to participants and presented without keywords, no differences emerged between the semantically informed condition and the naive condition in any of the the ERP components, all $|t|$s < `r max(abs(filter(contrast_table, phase == "Pre-insight")$t_value))`, all $p$s `r print_p(min(filter(contrast_table, phase == "Pre-insight")$p_value))` (Figure \@ref(fig:fig1)B--D).
This was expected given that the critical keywords (leading either to semantically informed perception or to naive perception) had not yet been presented, and given that the assignment of objects to conditions was counterbalanced across participants as to control for low-level visual differences.

@@

In an exploratory time-frequency analysis, we checked for differences in event-related power between semantically informed perception and naive perception within each of the three phases of the experiment.
Cluster-based permutation tests [@maris2007] revealed no significant clusters in the pre-insight phase (see Figure 2), all $p$s > `r print_p(min(filter(tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Naive")$p_val))`, but one significant cluster in the insight phase (see Figure 3), $p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Naive" & p_val < p_cluster)$p_val))`, and one significant cluster in the post-insight phase (see Figure 4), $p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Naive" & p_val < p_cluster)$p_val))`.
These two significant clusters in the insight and post-insight phases were similar in their direction, latency, frequency range, and topographic distribution.
Both clusters had a negative sign, started around 600 ms after object onset [but see @sassenhagen2019] and continued all the way until the end of the analyzed period at 1,400 ms.
They spanned a broad range of frequencies in the alpha and lower beta range as well as a broad set of channels, but appeared to be most focal at around 15 Hz and parietal channels.
Thus, semantically informed perception seems to alter not only early, evoked activity (see Event-Related Potentials above) but also later, induced activity, in the form of a reduction of post-stimulus power at parietal channels in the range of alpha and lower beta frequencies.

```{r, fig2, cache=!run$figures, fig.height=11, fig.cap="(ref:figure-2-caption)"}
# Create topographic plots for event-related power in the pre-insight phase
plot_tfr_topos(
  filter(tfr_grand_ave, phase == "Pre-insight"),
  filter(tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Naive"),
  p_cluster = p_cluster
)
```

(ref:figure-2-caption) Time-frequency results for the pre-insight phase.
Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the naive condition, grand-averaged across participants.
A cluster-based permutation test indicated no clusters for which this difference was statistically significant (all $p$s > `r print_p(min(filter(tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Naive")$p_val))`).

```{r, fig3, cache=!run$figures, fig.height=11, fig.cap="(ref:figure-3-caption)"}
# Create topographic plots for event-related power in the insight phase
plot_tfr_topos(
  filter(tfr_grand_ave, phase == "Insight"),
  filter(tfr_clusters, contrast == "Insight/Informed - Insight/Naive"),
  p_cluster = p_cluster
)
```

(ref:figure-3-caption) Time-frequency results for the insight phase.
Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the naive condition, grand-averaged across participants.
Black dots highlight EEG channels that were part of a cluster for which this difference was statistically significant ($p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Naive" & p_val < p_cluster)$p_val))`).

```{r, fig4, cache=!run$figures, fig.height=11, fig.cap="(ref:figure-4-caption)"}
# Create topographic plots for event-related power in the post-insight phase
plot_tfr_topos(
  filter(tfr_grand_ave, phase == "Post-insight"),
  filter(
    tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Naive"
  ),
  p_cluster = p_cluster
)
```

(ref:figure-4-caption) Time-frequency results for the post-insight phase.
Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the naive condition, grand-averaged across participants.
Black dots highlight EEG channels that were part of a cluster for which this difference was statistically significant ($p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Naive" & p_val < p_cluster)$p_val))`).

@@

Second, there is an alternative explanation specifically for the effects observed in the insight phase, when the objects were presented together with matching or non-matching keywords.
The N170 modulation might in fact not be due to semantic information changing the processing of objects in the semantically informed condition (as we had hypothesized), but rather a mismatch response to the objects in the naive condition.
The non-matching keywords might have primed participants to expect a certain set of visual features that did actually not come true once the object was displayed, potentially provoking a fast and strong brain response within the first 200 ms.
However, in a control analysis for this alternative explanation, we could show that the N170 effect in the insight phase does not depend on the naive condition.
For this control analysis, we contrasted the semantically informed condition (i.e., matching key words and participants indicating in their response that they knew what the object was or had an assumption) against a different control condition, namely, those objects that were presented with matching keywords (as in the semantically informed condition), but for which participants failed to capitalize on the keywords and instead indicated that they still did not know what kind of object they were viewing (a kind of "failed insight").
This was the case for an average of `r mean(objects_per_condition$Exclude_informed)` objects per participant (= `r percent(mean(objects_per_condition$Exclude_informed) / 60, accuracy = 0.1)` of objects presented with matching keywords).
Contrasting the semantically informed condition and the failed insight condition with matching key words, we again observed an enlarged (i.e., more negative) N170 component during semantically informed perception, $b$ = `r filter(contrast_table_control, component == "N170" & phase == "Insight")$estimate` µV, $t$(`r print_dof(filter(contrast_table_control, component == "N170" & phase == "Insight")$df)`) = `r filter(contrast_table_control, component == "N170" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "N170" & phase == "Insight")$p_value)`.
Likewise, the reduction of the N400 was replicated in this control analysis, $b$ = `r filter(contrast_table_control, component == "N400" & phase == "Insight")$estimate` µV, $t$(`r print_dof(filter(contrast_table_control, component == "N400" & phase == "Insight")$df)`) = `r filter(contrast_table_control, component == "N400" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "N400" & phase == "Insight")$p_value)`, as was the late reduction in event-related power ($p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Exclude_informed" & p_val < p_cluster)$p_val))`; see Supplementary Figure 1).
This adds credibility to the notion that these effects are specific to those objects for which participants experienced a moment of insight induced by semantic information.

@@

```{r, figs1, cache=!run$figures, fig.height=11, fig.cap="(ref:figure-s1-caption)"}
# Create topographic plots for control analysis of event-related power
plot_tfr_topos(
  filter(tfr_grand_ave, phase == "Insight"),
  filter(
    tfr_clusters, contrast == "Insight/Informed - Insight/Exclude_informed"
  ),
  p_cluster = p_cluster,
  condition_plus = "Informed",
  condition_minus = "Exclude_informed"
)
```

(ref:figure-s1-caption) Time-frequency results for the control analysis.
Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the "failed insight" condition (see Results: Control Analysis in the main text), grand-averaged across participants.
Black dots highlight EEG channels that were part of a cluster for which this difference was statistically significant ($p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Exclude_informed" & p_val < p_cluster)$p_val))`).

>>>>

The experiment consisted of three phases (see Figure 1A).
In the *pre-insight* phase, after written informed consent had been obtained and the EEG had been prepared, all 240 familiar and unfamiliar objects were presented once in random order and without any keywords.
Each trial consisted of a fixation cross presented in the middle of the screen for 0.5 s, followed by the presentation of the object until participants made a response or until a time out after 3 s.
The inter-trial interval was 0.5 s and participants took a self-timed break after each block of 60 objects.
The task, which was kept the same across all three phases of the experiment, was to classify each object using one of four response alternatives:
(a) *Ich weiß was das ist oder habe eine starke Vermutung* [I know what this is or have a strong assumption],
(b) *Ich habe eher eine Vermutung, was das ist* [I rather have an assumption what this is],
(c) *Ich habe eher keine Vermutung, was das ist* [I rather have no assumption what this is], or
(d) *Ich weiß nicht, was das ist, und habe auch keine Vermutung* [I don’t know what this is and have no assumption].
Participants were asked to respond as quickly and as accurately as possible by pressing one out of four buttons with the index or middle finger of their left or right hand, respectively.
The mapping of the rating scale to the four buttons (left to right or right to left) was counterbalanced across participants.

@@

```{r, fig1, cache=!run$figures, fig.height=12, fig.cap="(ref:fig1-caption)"}
# Create Figure 1
plot_fig1(files_dir, evokeds, config, channel_locations, models)
```

(ref:fig1-caption) Experimental design and ERP results.
***A***, In the pre-insight phase, participants were presented with 120 unfamiliar objects and indicated if they knew what kind of object they were viewing.
In the insight phase, half of these objects were presented with matching keywords (in red color for illustration), leading to semantically informed perception, and the other half with non-matching keywords (in blue color for illustration), leading to naive perception.
In the post-insight phase, the same objects were presented again without keywords.
***B***, ***C***, ***D***, ERP waveforms and scalp topographies for the P1 component (100--150 ms, ***B***), for the N170 component (150--200 ms, ***C***), and for the N400 component (400--700 ms, ***D***) for objects with semantically informed perception versus naive perception within the three different phases.
Semantically informed perception was associated with more negative amplitudes in the N170 component during the insight phase, less negative amplitudes in the N400 component during the insight and post-insight phases, and more positive amplitudes in the P1 component during the post-insight phase.
The time windows and channels for quantifying the ERP components are highlighted by the gray areas in the ERP waveforms and by the black markers on the scalp topographies, respectively.
Colored ribbons around the ERP waveforms show ± 1 standard error of the mean across participants.
Ampl. = amplitude.\newline
\* $p_\text{corr} < .05$. \*\* $p_\text{corr} < .01$. \*\*\* $p_\text{corr} < .001$.

@@

We first excluded from all further analyses those objects for which the participant had responded with "I know what this is" in the pre-insight phase (i.e., before any keywords were presented).
This led to the exclusion of an average of `r mean(objects_per_condition$Exclude_known)` objects per participant (= `r percent(mean(objects_per_condition$Exclude_known) / 120, accuracy = 0.1)` of all unfamiliar objects).
Next, to delineate semantically informed and naive perception, the assignment of the remaining objects to one of these two conditions was co-determined by our experimental manipulation (matching versus non-matching keywords) and the behavioral response of the participant in the insight phase (see Figure 1A).
Objects were assigned to the semantically informed condition if and only if they were presented with matching keywords and the participant responded with knowing what the object was or having an assumption.
This was the case for an average of `r mean(objects_per_condition$Informed)` objects per participant (= `r percent(mean(objects_per_condition$Informed) / 60, accuracy = 0.1)` of objects presented with matching keywords).
Complementarily, objects were assigned to the naive condition if and only if they were presented with non-matching keywords and the participant responded with not knowing what the object was or having rather no assumption.
This was the case for an average of `r mean(objects_per_condition$Naive)` objects per participant (= `r percent(mean(objects_per_condition$Naive) / 60, accuracy = 0.1)` of objects presented with non-matching keywords).
This same assignment of objects to conditions based on the insight phase was carried over to the pre-insight and post-insight phases for each participant individually.
This allowed us to test, on the one hand, if the objects from both conditions differed in important aspects even before any keywords were presented (pre-insight phase) and, on the other hand, if the semantic understanding acquired in the insight phase had any down-stream effects on the subsequent perception of the objects (post-insight phase).

@@

In the pre-insight phase, when objects were unfamiliar to participants and presented without keywords, no differences emerged between the semantically informed condition and the naive condition in any of the the ERP components, all $|t|$s < `r max(abs(filter(contrast_table, phase == "Pre-insight")$t_value))`, all $p$s `r print_p(min(filter(contrast_table, phase == "Pre-insight")$p_value))` (Figure 1B--D).
This was expected given that the critical keywords (leading either to semantically informed perception or to naive perception) had not yet been presented, and given that the assignment of objects to conditions was counterbalanced across participants as to control for low-level visual differences.

@@

In an exploratory time-frequency analysis, we checked for differences in event-related power between semantically informed perception and naive perception within each of the three phases of the experiment.
Cluster-based permutation tests [@maris2007] revealed no significant clusters in the pre-insight phase (see Supplementary Figure 1), all $p$s > `r print_p(min(filter(tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Naive")$p_val))`, but one significant cluster in the insight phase (see Figure 2), $p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Naive" & p_val < p_cluster)$p_val))`, and one significant cluster in the post-insight phase (see Figure 3), $p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Naive" & p_val < p_cluster)$p_val))`.
These two significant clusters in the insight and post-insight phases were similar in their direction, latency, frequency range, and topographic distribution.
Both clusters had a negative sign, started around 600 ms after object onset [but see @sassenhagen2019] and continued all the way until the end of the analyzed period at 1,400 ms.
They spanned a broad range of frequencies in the alpha and lower beta range as well as a broad set of channels, but appeared to be most focal at around 15 Hz and parietal channels.
Thus, semantically informed perception seems to alter not only early, evoked activity (see Event-Related Potentials above) but also later, induced activity, in the form of a reduction of post-stimulus power at parietal channels in the range of alpha and lower beta frequencies.

```{r, fig2, cache=!run$figures, fig.height=11, fig.cap="(ref:fig2-caption)"}
# Create topographic plots for event-related power in the insight phase
plot_tfr_topos(
  filter(tfr_grand_ave, phase == "Insight"),
  filter(tfr_clusters, contrast == "Insight/Informed - Insight/Naive"),
  p_cluster = p_cluster
)
```

(ref:fig2-caption) Time-frequency results for the insight phase.
Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the naive condition, grand-averaged across participants.
Black dots highlight EEG channels that were part of a cluster for which this difference was statistically significant ($p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Naive" & p_val < p_cluster)$p_val))`).

```{r, fig3, cache=!run$figures, fig.height=11, fig.cap="(ref:fig3-caption)"}
# Create topographic plots for event-related power in the post-insight phase
plot_tfr_topos(
  filter(tfr_grand_ave, phase == "Post-insight"),
  filter(
    tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Naive"
  ),
  p_cluster = p_cluster
)
```

(ref:fig3-caption) Time-frequency results for the post-insight phase.
Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the naive condition, grand-averaged across participants.
Black dots highlight EEG channels that were part of a cluster for which this difference was statistically significant ($p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Naive" & p_val < p_cluster)$p_val))`).

@@

Second, there is an alternative explanation specifically for the effects observed in the insight phase, when the objects were presented together with matching or non-matching keywords.
The N170 modulation might in fact not be due to semantic information changing the processing of objects in the semantically informed condition (as we had hypothesized), but rather a mismatch response to the objects in the naive condition.
The non-matching keywords might have primed participants to expect a certain set of visual features that did actually not come true once the object was displayed, potentially provoking a fast and strong brain response within the first 200 ms.
However, in a control analysis for this alternative explanation, we could show that the N170 effect in the insight phase does not depend on the naive condition.
For this control analysis, we contrasted the semantically informed condition (i.e., matching key words and participants indicating in their response that they knew what the object was or had an assumption) against a different control condition, namely, those objects that were presented with matching keywords (as in the semantically informed condition), but for which participants failed to capitalize on the keywords and instead indicated that they still did not know what kind of object they were viewing (a kind of "failed insight").
This was the case for an average of `r mean(objects_per_condition$Exclude_informed)` objects per participant (= `r percent(mean(objects_per_condition$Exclude_informed) / 60, accuracy = 0.1)` of objects presented with matching keywords).
Contrasting the semantically informed condition and the failed insight condition with matching key words, we again observed an enlarged (i.e., more negative) N170 component during semantically informed perception, $b$ = `r filter(contrast_table_control, component == "N170" & phase == "Insight")$estimate` µV, $t$(`r print_dof(filter(contrast_table_control, component == "N170" & phase == "Insight")$df)`) = `r filter(contrast_table_control, component == "N170" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "N170" & phase == "Insight")$p_value)`.
Likewise, the reduction of the N400 was replicated in this control analysis, $b$ = `r filter(contrast_table_control, component == "N400" & phase == "Insight")$estimate` µV, $t$(`r print_dof(filter(contrast_table_control, component == "N400" & phase == "Insight")$df)`) = `r filter(contrast_table_control, component == "N400" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "N400" & phase == "Insight")$p_value)`, as was the late reduction in event-related power ($p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Exclude_informed" & p_val < p_cluster)$p_val))`; see Supplementary Figure 2).
This adds credibility to the notion that these effects are specific to those objects for which participants experienced a moment of insight induced by semantic information.

@@

```{r, figs1, cache=!run$figures, fig.height=11, fig.cap="(ref:figs1-caption)"}
# Create topographic plots for event-related power in the pre-insight phase
plot_tfr_topos(
  filter(tfr_grand_ave, phase == "Pre-insight"),
  filter(tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Naive"),
  p_cluster = p_cluster
)
```

(ref:figs1-caption) Time-frequency results for the pre-insight phase.
Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the naive condition, grand-averaged across participants.
A cluster-based permutation test indicated no clusters for which this difference was statistically significant (all $p$s > `r print_p(min(filter(tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Naive")$p_val))`).

```{r, figs2, cache=!run$figures, fig.height=11, fig.cap="(ref:figs2-caption)"}
# Create topographic plots for control analysis of event-related power
plot_tfr_topos(
  filter(tfr_grand_ave, phase == "Insight"),
  filter(
    tfr_clusters, contrast == "Insight/Informed - Insight/Exclude_informed"
  ),
  p_cluster = p_cluster,
  condition_plus = "Informed",
  condition_minus = "Exclude_informed"
)
```

(ref:figs2-caption) Time-frequency results for the control analysis.
Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the "failed insight" condition (see Results: Control Analysis in the main text), grand-averaged across participants.
Black dots highlight EEG channels that were part of a cluster for which this difference was statistically significant ($p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Exclude_informed" & p_val < p_cluster)$p_val))`).
